\documentclass[defaultstyle,11pt]{thesis}

\usepackage{amssymb}		% to get all AMS symbols
\usepackage{amsmath}
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??
\usepackage{natbib}
\usepackage{rotating}

%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{Tools for the occurrence of free-living and symbiotic organisms in space and time}

\author{Maxwell B.}{Joseph}

\otherdegrees{B.S., University of California Davis, 2008}

\degree{Doctor of Philosophy}		%  #1 {long descr.}
	{Ph.D., Ecology and Evolutionary Biology}		%  #2 {short descr.}

\dept{Department of}			%  #1 {designation}
	{Ecology and Evolutionary Biology}		%  #2 {name}

\advisor{Prof.}				%  #1 {title}
	{Pieter T. J. Johnson}			%  #2 {name}

\reader{Prof. Vanja Dukic}

\readerThree{Prof. Samuel Flaxman}		%  3rd person to sign thesis

\readerFour{Prof. Andrew Martin}

\readerFive{Prof. Valerie McKenzie}

\abstract{  \OnePageChapter	% because it is very short
This doctoral dissertation broadly aims to improve methods for understanding the occurrence of organisms in space and time, including organisms that cause disease.
The processes that drive occurrence are often represented mathematically as ecological theories, which can be applied to uncover actionable insights into disease management.
This was a focus of my first chapter which characterized the gap between disease ecology theory and infectious disease management.
My second chapter focused on filling in a gap theoretically at the intersection of multi-host pathogens and host community disassembly.
Specifically, I construct a theoretical model to evaluate disease consequences when hosts are extirpated according to a variety of rules predicted from community ecology.
The third chapter develops a method to link representations of latent processes that drive species occurrence to observable (with error) data, with the goal of understanding multiple causal pathways in an occupancy model.
The fourth also extends occupancy models, but to allow for multi-host multi-symbiont (parasites included) systems.
Chapter five is somewhat different topically, focusing on missing species trait interpolation, but methodologically is not much of a departure, drawing on Bayesian hierarchical modeling as in the previous two chapters.
The final chapter develops a theoretical model to generate predictions about the effect of host diversity on the diversity and transmission of symbiotic organisms.
	}

\dedication[Dedication]{	% NEVER use \OnePageChapter here.
	To my family and friends, bipedal and otherwise.
	}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
None of this would have been possible without my loving family and friends. I would like to thank my labmates Joseph Mihaljevic, Sarah Orlofske,
Sara Paull,
Katherine Richgels,
Travis McDevitt-Galles,
Dan Preston,
Miranda Redmond,
Jazzmin Jenkins,
Dain Calhoun,
Will Stutz,
Sarah Haas,
Bethany Hoye,
Jason Hoverman,
Kim Medley, and
Yuri Springer. Many faculty have been gracious with their time including Nichole Barger,
John Basey,
Dean Bowers,
Kendi Davies,
Michael Grant,
Brett Melbourne,
Rebecca Safran,
Stacey Smith, and
Carol Wessman. Many fellow students have helped me along the way as well, including Aidan Beers,
Amanda Hund,
Amy Churchill,
Angela Boag,
Caroline Tucker,
Chris Steenbock,
Christine Avena,
Collin ”Schwan Quixote” Schwantes,
David Zonana,
Evelyn Cheng,
Gaurav Vaidya,
Helen McCreery,
Jeff McClenahan,
Joey Hubbard,
Jon Leff,
Jordan Keueneman,
Julian Resasco,
Kevin Bracy Knight,
Kika Tarsus,
Lauren Shoemaker,
Lisette Arellano,
Matt ”Marty Milkins” Wilkins,
Megan Blanchard,
Nathan Kleist,
Nora Connor,
Se Jin Song,
Teal Potter,
Tim Szewczyk,
Toby Hammer,
Topher Weiss-Lehman,
Tim Farkas, and
Ty Tuff.
	}

% \IRBprotocol{E927F29.001X}	% optional!

\ToCisShort	% use this only for 1-page Table of Contents

\LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures

\LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input macros.tex
\input chapter1.tex
\input chapter2.tex
\input chapter3.tex
\input chapter4.tex
\input chapter5.tex
\input chapter6.tex

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{apalike}	% or "siam", or "alpha", etc.
\bibliography{refs}		% Bib database in "refs.bib"

\end{document}
